---
description: |
  "This is a child document for README.Rmd to isolate What's New updates (last section of README)"
  "see README.Rmd's last chunk."
  "No need to knit this. Knitting README will automatically include this."
---

```{r setup-news, include=FALSE}
library(knitr)
opts_chunk$set( echo = TRUE, eval = FALSE, warning = FALSE, message = FALSE)
```


```{r, echo=FALSE, eval=FALSE, message='hide', fig.asp=1, out.width="50%"}
## template chunk - don't change/delete
```

## What's New

#### April 2023

* submitted to Bioconductor.

#### September 2024

* fixed bugs: the clash of functions from dependencies.

#### December 2025

* Added a `mode` argument to `PLSDA_batch()`.
* Added a `criterion` argument to `linear_regres()` to select P-values from the optimal model based on the specified criterion.
* Added a `return.model` arugument to `linear_regres()` to reduce memory usage when set to `FALSE`.
* Extended `Scatter_Density()` to support any multivariate method that returns component scores, including PCA and PLS, with corresponding arguments updated.
* Added `lighten()` and `darken()` functions for enhanced color generation.
* Refined multiple functions to improve usability.
* Updated the vignette accordingly.
